rough outline

### 2022-04-29 outline.Rmd
A little clean up
Changed countries

```{r}
#Mean total deaths from 1990-2017 of high-population countries
deaths_highpop_countries <- deaths_df %>% 
  filter(country %in% c('United States', 'Brazil', 'Ethiopia', 'Russia', 'China', 'Australia')) %>% 
  group_by(country) %>% 
  select(total_deaths) %>% 
  summarize(average_death_high = mean(total_deaths))

@@

#Mean total deaths from 1990-2017 of high-population countries
deaths_lowpop_countries<- deaths_df %>% 
  filter(country %in% c('Canada', 'Argentina', 'Seychelles', 'Romania', 'Israel', 'Tonga')) %>% 
  group_by(country) %>% 
  select(total_deaths) %>% 
  summarize(average_death_low = mean(total_deaths))

@@

```{r}
joined_df <- full_join(deaths_df, world_pop2, by = c("country" = "Country.Name"))
glimpse(joined_df)

```
```{r}
ggplot(joined_df, aes(fill=Count, y=country, x=year)) + 
  geom_bar(position="stack", stat="identity")

>>>>

```{r}
#Mean total deaths from 1990-2017 of high-population countries
deaths_highpop_countries <- deaths_df %>% 
  filter(country %in% c('United States', 'Brazil', 'Nigeria', 'Germany', 'Pakistan', 'Australia')) %>% 
  group_by(country) %>% 
  select(total_deaths) %>% 
  summarize(average_death_high = mean(total_deaths))

@@

#Mean total deaths from 1990-2017 of high-population countries
deaths_lowpop_countries<- deaths_df %>% 
  filter(country %in% c('Canada', 'Chile', 'Malawi', 'Serbia', 'Sri Lanka', 'New Zealand')) %>% 
  group_by(country) %>% 
  select(total_deaths) %>% 
  summarize(average_death_low = mean(total_deaths))

@@

```{r}
